\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-08-29 msnbase2.Rnw
add sentence about on-disk or im-mem (rev 3 suggestion)

>>>>

\textcolor{blue}{The on-disk backend has become the preferred backend
  for large data manipulation, and the only viable alternative for
  very large data (i.e. larger than the available RAM) and/or when
  several MS levels are to loaded and handled simultaneously. The
  on-disk backend can still prove useful in cases when small MS2-only
  data are to be analysed and will remain available in future versions
  of \texttt{MSnbase}.}
